A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-06-08 methodology.tex
two types

We define a code change to be a modification to a program's source code that changes the program's abstract syntax tree (AST). A change pattern is a set of code changes that serves a specific purpose. Purposes include rectifying program behaviour with respect to a specific functional or non-functional requirement (bug-fixing patterns) as well as improving code readability or maintainability (refactoring patterns). In this work, we are interested in bug-fixing patterns. Thus, from now on, whenever we refer to code patterns, we mean bug-fixing patterns.

>>>>

We define a code change to be a modification to a program's source code that changes the program's abstract syntax tree (AST). A change pattern is a set of code changes that serves a specific purpose. Purposes include rectifying program behaviour with respect to a specific functional or non-functional requirement (bug-fixing patterns) and changes that support bug-fixing patterns (fix-induced patterns) as well as improving code readability or maintainability (refactoring patterns). In this work, we are interested in bug-fixing and fix-induced patterns. Thus, from now on, whenever we refer to code patterns, we mean bug-fixing and fix-induced patterns.
